Macro Impacts

### 2016-07-23 Macro Impacts Revised.tex
Program mostly figured out.

\pagebreak
\section{Melt Zone}
As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
\begin{align}
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
\end{align}
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.

>>>>

\section{The Procedure Made More Explicit}
\item We wish to consider a line source. First, determine the number $N$ of point sources with which we want to approximate the line.
\item Next we determine the coordinates of these points. If the Earth has radius $R_E$, and the line is a distance $D$ from the center, then the length of the line intersecting the earth is $L=2\sqrt{R_E^2-D^2}$. we must space the points evenly, so each point will be $\f{L}{N}$ apart from one another. To maintain symmetry, we insist that $N$ be odd, and that one point exist in the plane of symmetry. The coordinate of the center point is $(x,y,z)=(0,D,0)$. The set of points is described as $P=\{(x,D,0):x=\f{L}{N}(n-\f{N-1}{2}),n=\{0,\dots,N\}\}$\,.
\item Now that we have a set of points, we must describe the set of rays originating at those points. The website listed above has a nice set of optimally spaced points on spheres, so we will use that. We will import the coordinates of the points from a text document. In order to apply our methods, we need to rotate the ray into the $xy$-plane. Suppose we want to propagate the ray whose coordinates w.r.t the starting point are
(x,y,z)=\p{\f{L}{N}\p{n_0-\f{N-1}{2}},D,0}\,.
in the direction $(a,b,c)$ (given by the text document). We need to take this to a point of the form $(x,0)$. It is clear that
x_0=\sqrt{\f{L^2}{N^2}\p{n_0-\f{N-1}{2}}^2+D^2}
where the rotation is by the angle
\alpha=\arctan\p{\f{L}{ND}\p{n_0-\f{N-1}{2}}}
and whose matrix is
\mat{ccc}{\cos\alpha&0&\sin\alpha\\0&1&0\\-\sin\alpha&0&\cos\alpha}\,.
In this new frame, the initial coordinate of the ray is in the $xy$-plane. The direction of propagation, however, may not be. In this new frame, the ray propagates as
\mat{c}{a'\\b'\\c'}=\mat{ccc}{\cos\alpha&0&\sin\alpha\\0&1&0\\-\sin\alpha&0&\cos\alpha}\mat{c}{a\\b\\c}
We now rotate so that the $z$ coordinate is zero, and we extract the angle $\alpha$. The angle we want to rotate by is
\beta=\arctan\p{\f{c'}{b'}}\,,
and the rotation matrix is
\mat{ccc}{1&0&0\\0&\cos\beta&-\sin\beta\\0&\sin\beta&\cos\beta}\,.
We now have a propagation direction in the $xy$-plane:
\mat{c}{a''\\b''\\c''}=\mat{ccc}{1&0&0\\0&\cos\beta&-\sin\beta\\0&\sin\beta&\cos\beta}\mat{c}{a'\\b'\\c'}\,.
\section{Melt Zone}
As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.
